Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-02-07 analysis/paper/paper.Rmd
age adaptation done

## Symptoms
```{r}
testInsectsbinomialTab$symptoms[,-7] %>% knitr::kable()
plotSympt
```

@@

@@

@@

```{r}
mosaic(d_severity_rm~d_elicitor_gr5,data=rdb)

>>>>

## Symptoms
```{r}
testInsectsbinomialTab$symptoms[,-7] %>% knitr::kable()
```

```{r}
plotSympt
```

Patients who underent anaphylaxis due to insect venom more often experienced 
cardiologic symptoms. Especially collapsing due to hypotension was prominently 
more often seen in patient who underwent venom anaphylaxis. This difference was especially visible in children under the age of 18 years.

@@

## Diagnostics

@@

Cardiologic symptoms and hypotensive collapse might be associated with vanom anaphylaxis due to the vaso-vagal reflex. As seen in patients undrgoing blood sampling needles (and probably also insect stings) may elicit a hypotensive response due to extreme emotional distress with bradycardia, limiting the bloodflow to the brain and causing a syncope. This mechanism may contribute to the ongoing histamin-induced vasodialation and may worsen the symptoms of an allergic reaction.

@@

```{r}
mosaic(d_severity_rm~d_elicitor_gr5,data=rdb)
```

```{r}
hypotensionPlot
```

```{r}
cramerPlot
```
